Equalizer 2.0\\Convergence of a Parallel Rendering Framework

### 2017-04-03 paperIEEE.tex
Tweak
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@43 db7c848b-7755-4df2-b763-8796797afa52
Minor introducation tweak
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@44 db7c848b-7755-4df2-b763-8796797afa52

Furthermore, various applications and frameworks have used \textsf{Equalizer}
for new research in visualization, such as \textsf{RTNeuron}~\cite{HBBES:13}, an
OpenGL renderer for visualizing simulations of neurocortical brain regions;

\textsf{Omegalib}~\cite{Omegalib}, extending \textsf{Equalizer} for the hybrid
2D/3D environments such as the CAVE2;

@@

\begin{figure*}[ht]\center
  \includegraphics[width=\textwidth]{images/spikesdist}
  \caption{\label{fSpikesDist}Object mapping (left )and data synchronization
    times (middle, detail view right) for the spike volume data set in
    \fig{fVolumes}, right}
\end{figure*}

>>>>

Furthermore, various applications and frameworks have used \textsf{Equalizer}
for new research in visualization, such as \textsf{RTNeuron}~\cite{HBBES:13}, an
OpenGL renderer for visualizing simulations of neurocortical brain regions;
\textsf{Omegalib}~\cite{Omegalib}, a framework used in the Cave2, extending
\textsf{Equalizer} for hybrid collaborative 2D/3D environments;

@@

\begin{figure*}[ht]\center
  \includegraphics[width=\textwidth]{images/spikesdist}
  \caption{\label{fSpikesDist}Object mapping (left) and data synchronization
    times (middle, detail view right) for the spike volume data set in
    \fig{fVolumes}, right}
\end{figure*}
